---
output: 
  github_document: default
  beamer_presentation: default
  ioslides_presentation: default
---


---
title: 'Capstone Project Proposal '
author: "Maria Leite"
date: "November 7, 2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
```{r}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
* 	**What is the problem you want to solve?**

The project has a two- fold goal: one is addressing the problem of a multi-lingual classification of cooking recipe ingredients, the other  is  designing a recommendation system of recipe or ingredient.

*	 **Who is your client and why do they care about this problem?
In other words, what will your client DO or DECIDE based on your analysis that they wouldn't have otherwise?**

The problem is a task integrated into a benchmarking initiative of CRWB (Cooking Recipes Without Border) research group dedicated to the evaluation of new algorithms and technologies for cooking recipe recommendation, access, and exploration. It offers tasks to the research community that are related to human and social aspects of cooking recipe and healthy eating decision-making.
The CRWB initiative answers the current need to address the multitude of research questions intersecting Data Sciences, Intelligent Food and Cooking Recipe in the context of Big Data. Nowadays, food, healthy eating and new recipes have become one of the central subjects in our daily life. There is an extensive growth of food variety, ingredient combinations, and number of recipes, even IBM supercomputers are generating new recipes, notwithstanding   food selection still leads to poor health conditions. On the other hand, the growth of data seems to out-speed the advance of the many established data science technologies. Therefore, the CRWB is a leading initiative for the relevant communities to make contributions in the analysis and design of models, methods, algorithms, and intelligent tools to support the data management and analysis as well as research in human and social aspects of cooking recipe and healthy eating decision-making. Additionally, it will define future research directions in the field.

* 	**What data are you going to use for this? How will you acquire this data?**

The project will use a sample of the CRWB data set being built from the recipe
collection of Mrs. Nicole Andres's asset since April 2016 under the CC BY-NC-ND License 4.
Each CRWB cooking recipe is based on ingredients and list of actions to prepare the related
dish.  The data will be provided by the CRBW research team.

*	**In brief, outline your approach to solving this problem (knowing that this might change later).**

The first task is to use R and Data Wrangling techniques to explore the data so to identify: a) the most adequate classification techniques that can be used and b) the data manipulations that need to be performed before applying the methods identified in a).
Then, test the different classification techniques / algorithms to select the most efficient using a subset of the CRWB data sample mentioned above. Most likely this step will be an iterative process and will be performed using R. The identified classification technique will be applied to the whole CRBW data sample. The last part of the project will be dedicated to study and select algorithms for building a recommender system.  

*    **What are your deliverables? Typically, this would include code, along with a paper and/or a slide deck.**

The possible deliveries are: 1) codes along with a paper, 2) a recommender system.


